---
title: "Barcode Generation - Liu Method"
output:
  html_document:
    df_print: paged
---

```{r}
##Original code from Dr. Liu
setwd("/Users/yshibata/Documents/GitHub/MPRAdesign")
library(rareGWAMA);
mirna <- as.vector(unlist(as.data.frame(fread(file='HumanmiRNAseedsF.fasta',header=F,sep='\t'))));
mirna.new <- gsub('U',"T",mirna)
generate.kmer <- function(k=10,n=100) {
  freq <- list(A=.25,T=.25,G=.25,C=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',collapse='');
    is.mirna <- (length(grep(seq.tmp, mirna.new))>0);
    
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('TTTT',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}

kmer <- generate.kmer();
print(kmer)
```

`
sleep_for_a_minute <- function() {generate.kmer}
start_time <- Sys.time()
sleep_for_a_minute()
end_time <- Sys.time()
end_time - start_time
`
seq.tmp <- paste(seq.vec,sep='',coillapse='');
    is.mirna <- (length(grep(seq.tmp, mirna.new))>0);
    
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('TTTT',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);

```{r}
generate.kmer <- function(k=10,n=100) {
  freq <- list(A=.25,T=.25,G=.25,C=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
  }
  
}
generate.kmer

sleep_for_a_minute <- function(generate.kmer)
start_time <- Sys.time()
sleep_for_a_minute()
end_time <- Sys.time()
end_time - start_time
```

setwd("/Users/yshibata/Documents/GitHub/MPRAdesign")
library(rareGWAMA);
mirna <- as.vector(unlist(as.data.frame(fread(file='HumanmiRNAseedsF.fasta',header=F,sep='\t'))));
mirna.new <- gsub('U',"T",mirna)
generate.kmer <- function(k=10,n=1000) {
  freq <- list(A=.25,T=.25,G=.25,C=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',coillapse='');
    is.mirna <- (length(grep(seq.tmp, mirna.new))>0);
    
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('CCCC',seq.tmp),
                            grep('GGGG',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}
kmer <- generate.kmer();
write.csv(barcodes,'/Users/yshibata/Documents/GitHub/20bpMPRAdesign/20bpbarcodes.csv')
`
##header -> true or false?

```{r}
##mRNA processee not properly
setwd("/Users/yshibata/Documents/GitHub/20bpMPRAdesign")
library(rareGWAMA);
mirna <- as.vector(unlist(as.data.frame(fread(file='HumanmiRNAseedsF.fasta',header=T,sep='\t'))));
mirna.new <- gsub('U',"T",mirna)

TFBS.new <- as.vector(unlist(as.data.frame(fread(file='TFBSChiPBase.fasta',header=T,sep='\t'))));

generate.kmer <- function(k=20,n=1000) {
  freq <- list(A=.25,T=.25,G=.25,C=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',collapse='');
    is.mirna <- (length(grep(seq.tmp, mirna.new))>0);
    is.TFBS <- (length(grep(seq.tmp, TFBS.new))>0);
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('CCCC',seq.tmp),
                            grep('GGGG',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.TFBS==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.TFBS>0) print(c('overlap with TFBS', seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}

kmer <- generate.kmer();
print(kmer)
write.csv(kmer,'/Users/yshibata/Documents/GitHub/20bpMPRAdesign/LoopTest.csv')
```

`

```{r}
##worked
setwd("/Users/yshibata/Documents/GitHub/20bpMPRAdesign")
library("Biostrings")
library("tidyverse")
library("universalmotif")
library("TFBSTools")
library("rareGWAMA")

allSeeds <- readRNAStringSet("HumanmiRNAseedsF.fasta")
allSeedsmRNA <- Biostrings::reverseComplement(allSeeds)
allSeedsDNA <- DNAStringSet(allSeedsmRNA) %>% unique
seedSeqs <- allSeedsDNA %>% subseq(2, 7) %>% unique

allTFBS <- readDNAStringSet("TFBSChiPBase.fasta")
allTFBSDNA <- DNAStringSet(allTFBS)

generate.kmer <- function(k=20,n=1000) {
  freq <- list(A=.25,T=.25,G=.25,C=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',collapse='');
    is.mirna <- (length(grep(seq.tmp,seedSeqs))>0);
    ##write a loop -> the opposite comparison
    is.TFBS <- (length(grep(seq.tmp,allTFBSDNA))>0);
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('CCCC',seq.tmp),
                            grep('GGGG',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.TFBS==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.TFBS>0) print(c('overlap with TFBS', seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}

kmer <- generate.kmer();
print(kmer)
```
`
 for(val in seq.tmp) {
        if(val contains(seedS))
      }
`
```{r}
setwd("/Users/yshibata/Documents/GitHub/20bpMPRAdesign")
library("Biostrings")
library("tidyverse")
library("universalmotif")
library("TFBSTools")
library("rareGWAMA")

allSeeds <- readRNAStringSet("HumanmiRNAseedsF.fasta")
allSeedsmRNA <- Biostrings::reverseComplement(allSeeds)
allSeedsDNA <- DNAStringSet(allSeedsmRNA) %>% unique
seedSeqs <- allSeedsDNA %>% subseq(2, 7) %>% unique

generate.kmer <- function(k=20,n=1000) {
  freq <- list(A=.25,T=.25,C=.25,G=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',collapse='');
    
    ##create a loop for RNA & TFBS
    haveSeedlist <- match(seedSeqs,seq.tmp);
    is.mirna <- (length(haveSeedlist)>0);
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('CCCC',seq.tmp),
                            grep('GGGG',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}
system.time(generate.kmer())

```
`
```{r}
##Modification with loop
setwd("/Users/yshibata/Documents/GitHub/20bpMPRAdesign")
library("Biostrings")
library("tidyverse")
library("universalmotif")
library("TFBSTools")
library("rareGWAMA")

allSeeds <- readRNAStringSet("HumanmiRNAseedsF.fasta")
allSeedsmRNA <- Biostrings::reverseComplement(allSeeds)
allSeedsDNA <- DNAStringSet(allSeedsmRNA) %>% unique
seedSeqs <- allSeedsDNA %>% subseq(2, 7) %>% unique

allTFBS <- readDNAStringSet("TFBSChiPBase.fasta")
allTFBSDNA <- DNAStringSet(allTFBS)

generate.kmer <- function(k=10,n=1000) {
  freq <- list(A=.25,T=.25,C=.25,G=.25)
  kmer <- 0;
  ii <- 1;
  while(ii<=n) {
    
    seq.vec <- sample(c('A','T','G','C'),k,replace=T,prob=freq);
    seq.tmp <- paste(seq.vec,sep='',collapse='');
    
    ##create a loop for RNA & TFBS
    haveSeedlist <- match(seedSeqs,seq.tmp);
    is.mirna <- (length(haveSeedlist)>0);
    haveTFBSlist <- match(allTFBSDNA,seq.tmp);
    is.TFBS <- (length(haveTFBSlist)>0);
    is.polymer <- (length(c(grep('AAAA',seq.tmp),
                            grep('TTTT',seq.tmp),
                            grep('CCCC',seq.tmp),
                            grep('GGGG',seq.tmp)))>0);
    is.4 <- (length(unique(seq.vec))==4)
    if(is.mirna==0 & is.TFBS==0 & is.polymer==0 & is.4==1) {
      kmer[ii] <- seq.tmp;
      ii <- ii+1;
    }
    if(is.mirna>0) print(c('overlap with mirna',seq.tmp));
    if(is.TFBS>0) print(c('overlap with TFBS', seq.tmp));
    if(is.polymer>0) print(c('polymer',seq.tmp));
    if(is.4==0) print(c('not all 4',seq.tmp));
  }
  return(kmer);
}

kmer <- generate.kmer();
print(kmer)
```

write.csv(kmer,'/Users/yshibata/Documents/GitHub/20bpMPRAdesign/10bpbarcodesX1000.csv')
##save in file at the end